---
title: "Extract linear covariates from MixSIAR"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r setup}
library("tidyverse")
library("MixSIAR")
```

load up and run a quick model of the XXX example which includes a linear covariate.

```{r lake-example}


# Replace the system.file call with the path to your file
mix.filename <- system.file("extdata", "lake_consumer.csv", package = "MixSIAR")

mix <- load_mix_data(filename=mix.filename,
                     iso_names=c("d13C","d15N"),
                     factors=NULL,
                     fac_random=NULL,
                     fac_nested=NULL,
                     cont_effects="Secchi.Mixed")

# Replace the system.file call with the path to your file
source.filename <- system.file("extdata", "lake_sources.csv", package = "MixSIAR")

source <- load_source_data(filename=source.filename,
                           source_factors=NULL,
                           conc_dep=FALSE,
                           data_type="raw",
                           mix)

# Replace the system.file call with the path to your file
discr.filename <- system.file("extdata", "lake_discrimination.csv", package = "MixSIAR")

discr <- load_discr_data(filename=discr.filename, mix)


```

Create the jags model. This is where we can play with different types of explanatory variables and random effects. NOte that i am not evaluating this chunk by default as it takes a few mins to run. When run it save the ouput to an *.rda file which is loaded in the next chunk.

```{r jags-model, eval = FALSE}

# Write the JAGS model file
model_filename <- "MixSIAR_model.txt"
resid_err <- TRUE
process_err <- FALSE
write_JAGS_model(model_filename, resid_err, process_err, mix, source)

jags.1 <- run_model(run="very short", mix, source, discr, model_filename, 
                    alpha.prior = 1, resid_err, process_err)

save(jags.1, file = "jags.1.rda", compress = "xz")

```

Explore the contents of the output object, so we can find the linear effects terms!

```{r process-data}

# load the data
load("jags.1.rda")

output_options = list(summary_save = FALSE,
  summary_name = "summary_statistics", sup_post = FALSE, plot_post_save_pdf =
  FALSE, plot_post_name = "posterior_density", sup_pairs = FALSE,
  plot_pairs_save_pdf = FALSE, plot_pairs_name = "pairs_plot", sup_xy = FALSE,
  plot_xy_save_pdf = FALSE, plot_xy_name = "xy_plot", gelman = FALSE, heidel =
  FALSE, geweke = FALSE, diag_save = FALSE, diag_name = "diagnostics",
  indiv_effect = FALSE, plot_post_save_png = FALSE, 
  plot_pairs_save_png = FALSE,
  plot_xy_save_png = FALSE)

# source the plotting file we will modify
source("plot_continuous_var_combine.R")
plot_continuous_var_combine(jags.1, mix, source, output_options)

# output_JAGS(jags.1, mix, source, output_options)

```






